Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)

### 2025-08-05 resubmission/01-introduction.qmd
review introduction & antecedentes

Since 1980, economic inequality and wealth concentration have dramatically increased worldwide, becoming one of the main challenges for the social sciences. Globally, in 2021, less than 50% of the world population owned only 2% of the wealth, while the richest 10% concentrated 76%. Futhermore, the wealthiest 1% captured nearly 38% of total assets [@chancel_world_2022]. This context of economic disparity has sparked renewed interest in studying not only the objective aspects of inequality, such as income and access to resources, but also its subjective dimensions, including perceptions, beliefs, and associated attitudes [@janmaat_subjective_2013]. Such dimensions are deemed as key to understand the political delegitimation that economic inequality can elicit [@castillo_perception_2022]. Therefore, understanding how people perceive inequality is crucial, as these perceptions can influence how societies comprehend and justify (or not) inequality in the distribution of goods and services, as well as their capacity to funnel political discontent and eventually opposition to the current economic distribution.

The justification of economic inequality has a long tradition in sociology, with seminal works such as the ones from Kluegel [-@kluegel_social_1995a; -@kluegel_beliefs_1986] and Lane [-@lane_political_1962; -@lane_market_1986]. Lane's main aim was to "help explain the tenacious hold of market capitalism on the public mind" [-@lane_market_1986, p.384], proposing the distinction between market and political justice. Whereas political justice refer to government actions aligned with justice principles such equality or need, market justice involves the allocation linked to earned desserts, particularly through individual contributions based on as effort and ability. Sociological survey research in this area has considered questions related to the extent to which it is considered just to get better access to social services (such as pensions, health and education) based on payment capacity [@busemeyer_skills_2014; @immergut_it_2020; @castillo_socialization_2024; @koos_moral_2019; @lindh_bringing_2023; @lindh_public_2015]. Although these services could be considered basic rights of citizens, evidence to date suggests that a significant portion of the population justifies inequality in these areas [@koos_moral_2019] and that such preferences vary according to objective socioeconomic factors and the contextual characteristics of countries [@lindh_public_2015; @busemeyer_skills_2014]. In the present paper, we argue that there are two other relevant factors to take into account when analyzing differences between individuals and groups to this regard: the perception of economic inequality and the perception of meritocracy.

The perception of economic inequality can be understood as an individual's subjective assessment of how resources are allocated among members of a given society [@akyelken_urban_2020]. Regardless of their measurement, various studies have shown that this perception often underestimates the gap between the rich and the poor, revealing inconsistencies between objective and subjective aspects of inequality [@trump_income_2018]. Moreover, there is consistent evidence that perceived inequality, even under control of objective inequality, could have implications for attitudes toward the distribution of goods and services [@castillo_perception_2022; @schroder_income_2017], redistributive preferences, justification of inequality, and legitimacy of the economic system [@castillo_perception_2022; @garcia-sanchez_perceptions_2018; @garcia-sanchez_attitudes_2020]. From this perspective, in this paper we argue that perceptions of economic inequality may play a relevant aspect for understanding market justice preferences, as a lower perceived inequality could reinforce the idea that the differences in access to social services could be justified --- a link that becomes difficult to hold when high inequality is perceived.

Along with perception of inequality, a second focus of this paper is the perception of meritocracy. Meritocracy posits that inequality can be legitimized through distributive criteria such as effort and talent [@young_rise_1962; @davis_principles_2001]. Previous studies have demonstrated that people with stronger meritocratic beliefs tend to perceive less inequality as they attribute economic differences to individual achievements [@mijs_paradox_2021; @wilson_role_2003] and also to justify more inequality as these beliefs are associated with attitudes that legitimize status differences [@batruch_belief_2023]. In a context as Chile, where the distribution of goods and services is predominantly governed by market logics strongly introduced during the military dictatorship (1973-1989) [@madariaga_three_2020; @boccardo_30_2020], meritocratic perceptions have the potential to affect the acceptance of social inequalities. Therefore, incorporating the perception of meritocracy in this literature allows for an understanding of how attitudes toward inequality are shaped not only by the perception of economic gaps, but also by beliefs about how these gaps are justified. Furthermore, these beliefs are often consolidated from an early age, reinforced by institutions promoting values such as effort and individual skills to climb socially [@castillo_socialization_2024; @reynolds_perceptions_2014].

At this point we can propose the following research questions: To what extent the preferences for market justice are associated with perceptions of inequality and meritocracy? How stable are these associations (within subjects) along time? The primary objective of this study is to analyze the interplay between perceptions of inequality and meritocracy and their joint influence on preferences for market justice along time in Chile using the panel survey ELSOC (Social Chilean Longitudinal Study, 2016-2023). The chilean case appears as a particular case for studying market justice preferences given their story of high inequality and strong free-market policies introduced in the dictatorship period [@madariaga_three_2020; @flores_top_2020]. Additionally, this analysis seeks to explore how political and social contingencies---such as the 2019 and 2022 social movements---might have moderated these relationships by prompting more critical reflection on the commodification of social services [@somma_no_2021]. Recognizing the temporal dimension in shaping market justice preferences is essential, given that historical and contextual factors that could challenge or reaffirm the way in which individuals persceive inequality and meritocracy, and consequantely --- following our argument --- the preferences for market justice.

>>>>

Since 1980, economic inequality and wealth concentration have dramatically increased worldwide, becoming one of the main challenges for the social sciences. Globally, in 2021, less than 50% of the world population owned only 2% of the wealth, while the richest 10% concentrated 76%. Futhermore, the wealthiest 1% captured nearly 38% of total assets [@chancel_world_2022]. This context of economic disparity has sparked renewed interest in studying not only the objective aspects of inequality, such as income and access to resources, but also its subjective dimensions, including perceptions, beliefs, and associated attitudes [@janmaat_subjective_2013]. Such dimensions are deemed as key to understand the  delegitimation of political institutions that economic inequality can elicit [@castillo_perception_2022]. Therefore, understanding how people perceive inequality is crucial, as these perceptions can influence how societies comprehend and justify (or not) inequality in the distribution of goods and services, as well as their capacity to funnel political discontent and eventually opposition to the current economic distribution.

The justification of economic inequality is a topic with a long tradition in sociology, with seminal works such as the ones from Kluegel [-@kluegel_social_1995a; -@kluegel_beliefs_1986] and Lane [-@lane_political_1962; -@lane_market_1986]. Lane's main aim was to "help explain the tenacious hold of market capitalism on the public mind" [-@lane_market_1986, p.384], proposing the distinction between market and political justice. Whereas political justice refer to government actions aligned with justice principles such equality or need, market justice involves the allocation linked to earned desserts, particularly through individual contributions based on individual merit. Part of this agenda has focused on analyzing the extent to which individuals consider as just to get better access to social services (such as pensions, health and education) based on payment capacity [@busemeyer_skills_2014; @immergut_it_2020; @castillo_socialization_2024; @koos_moral_2019; @lindh_bringing_2023; @lindh_public_2015], usually under the label of market justice preferences. The empirical evidence to date suggests that a significant portion of the population justifies inequality in these areas [@koos_moral_2019], and that such preferences vary according to objective socioeconomic factors and countries contextual characteristics [@lindh_public_2015; @busemeyer_skills_2014]. Within this framework, we argue that there are two relevant factors that are usually sidelined in this literature and that are key to understand market justice preferences: the perception of economic inequality and the perception of meritocracy.

The perception of economic inequality can be understood as an individual's subjective assessment of how resources are allocated among members of a given society [@akyelken_urban_2020]. Regardless of their measurement, various studies have shown that this perception often underestimates the gap between the rich and the poor, revealing inconsistencies between objective and subjective aspects of inequality [@trump_income_2018]. Moreover, there is consistent evidence that perceived inequality, even under control of objective inequality, could have implications for attitudes toward the distribution of goods and services [@castillo_perception_2022; @schroder_income_2017], redistributive preferences, justification of inequality, and legitimacy of the economic system [@castillo_perception_2022; @garcia-sanchez_perceptions_2018; @garcia-sanchez_attitudes_2020]. From this perspective, in this paper we argue that perceptions of economic inequality would play a relevant role for understanding market justice preferences, as a lower perceived inequality could reinforce the idea that the differences in access to social services could be justified --- a link that becomes harder to hold when high inequality is perceived.

Along with perception of inequality, a second focus of this paper is the perception of meritocracy. Meritocracy posits that inequality can be legitimized through distributive criteria such as effort and talent [@young_rise_1962; @davis_principles_2001]. Previous studies have shown that those with stronger meritocratic perceptions tend to justify larger inequality, as economic differences are legitimized by being attributed to individual achievements [@mijs_paradox_2021; @wilson_role_2003; @batruch_belief_2023]. We argue that in contexts where the distribution of goods and services is predominantly governed by market logics, as in the chilean case [@madariaga_three_2020; @boccardo_30_2020], meritocratic perceptions could play a role in the preferences of market justice.

The primary objective of this study is to analyze the interplay between perceptions of inequality and meritocracy and their joint influence on preferences for market justice along time in Chile using the panel survey ELSOC (Social Chilean Longitudinal Study, 2016-2023). Furthermore, we explore how political and social contingencies---such as the 2019 and 2022 social movements---might have moderated these relationships by prompting more critical reflection on the commodification of social services [@somma_no_2021]. Recognizing the temporal dimension in shaping preferences is essential, given that historical and contextual factors that could challenge or reaffirm the way in which individuals perceive inequality and meritocracy, resulting in changes in market justice preferences.

### 2025-08-05 resubmission/02-antecedents.qmd
review introduction & antecedentes

# Theoretical views on market justice, inequality perception, and meritocracy

## The justification of market inequality

@@

Empirical studies have shown different strategies for the study of market justice preferences. A common approach in the literature is to gauge attitudes toward the legitimacy of inequality in specific domains, especially when linked to income differences. This can be traced to the seminal work of Kluegel and Smith [-@kluegel_beliefs_1981] who assessed the normative foundations that explain public support for economic inequality. Over time, this approach has been extended beyond income to include other market-mediated outcomes, such as education, healthcare, and/or pensions. For example, @vondemknesebeck_are_2016 and Immergut and Schneider [-@immergut_it_2020] examine whether citizens consider it fair that individuals with higher incomes can access better healthcare, while Lee and Stacey [-@lee_fairness_2023] apply a similar method in the context of education in Australia. These studies usually rely on a survey item asking respondents to evaluate the fairness of income-based access to welfare services, allowing for comparing justice perceptions across different contexts. Similarly, comparative studies have also considered these indicators to study the support for market-based distribution in welfare systems [@svallfors_political_2007;@lindh_public_2015]. More recently, Castillo et al. [-@castillo_socialization_2024] introduced a single-item composite measure of market justice to assess student attitudes toward income-based access to education, healthcare, and pensions in Chile. These empirical strategies all aim to capture the extent to which individuals accept inequality when framed as a reflection of market outcomes.

The study of market justice preferences has increasingly focused on how they are shaped by individuals' socioeconomic position, normative beliefs, and the institutional context in which they are embedded. Across the literature, there is empirical evidence suggesting that individuals in more advantaged socioeconomic positions---those with higher occupational class, income, and education---are more likely to support market justice principles [@svallfors_political_2007; @koos_moral_2019; @lindh_public_2015]. This tendency reflects not only material self-interest but also a broader moral economy, in which winners of the market system internalize justifications for the status quo. At the same time, political ideology also plays a role ---such as economically conservative values ---  where more right-wing individuals show higher support for meritocracy and more skepticism towards redistribution. This is particularly salient in countries with more restricted public provision of social services. For example, Castillo et al. [-@castillo_socialization_2024] in Chile and, Lee and Stacey [-@lee_fairness_2023] in Australia show that right-wing individuals are more supportive of market-based distribution of welfare. Beyond individual characteristics, country-level institutions also play a central role. In liberal welfare regimes like those of the United States or the United Kingdom, market justice preferences are more widespread, while in coordinated or social-democratic regimes---such as Sweden or Germany---citizens are generally more critical of market-based inequalities [@immergut_it_2020; @lindh_public_2015]. These findings suggest that market justice is also shaped contextually, which is represented by the development of welfare institutions, in line with the policy-feedbacks literature [@campbell_policy_2012; @pierson_when_1993].

## Perception of inequality

Perceptions of inequality have been associated with a range of distributive attitudes [@castillo_perception_2022; @garcia-sanchez_vicious_2019; @trump_income_2018; @mccall_exposure_2017]. Research indicates that perceptions of inequality influence redistributive preferences to a greater extent than objective or actual economic inequality [@gimpelson_misperceiving_2018]. Others have shown that the perception of inequality, through the perceived wage gap, is related to the justification of greater inequality [@Castillo2011]. In that sense, lower perceived inequality can reinforce support for market-based distributive arrangements by suggesting that the system is fair and that outcomes reflect effort and ability [@kuhn_eye_2011]. In contrast, when inequality is perceived as excessive or structurally determined, individuals could question the legitimacy of market justice and become more supportive of redistributive policies [@garcia-sanchez_vicious_2019].

@@

Among the different approaches to measuring perceived inequality, one of the most widely used is the estimation of wage gaps between occupational extremes, such as between a CEO and a manual worker. This type of item provides a concrete frame that respondents can relate to more easily than abstract questions about national income distribution [@castillo_percepcion_2019; @easterbrook_social_2021; @willis_legitimacy_2015]. While it enables the estimation of inequality using simple heuristics, this method is not without challenges. For instance, people often lack reliable knowledge about the earnings of those at the top of the income ladder, which leads to high variability in responses and the use of biased mental shortcuts [@knell_perceptions_2020]. Despite this, perceived wage gaps are strong predictors of political attitudes [@pedersen_attitudes_2019; @garcia-sanchez_perceptions_2018], making them a valuable tool for understanding public responses to economic disparities.

Another relevant critique of this approach lies in its conflation of different psychological constructs. Many surveys assess perceived inequality through Likert-type items that ask respondents to agree or disagree with statements, such as "income differences are too large," which captures general concern or discomfort rather than a specific perception [@Castillo2011; @garcia-sanchez_vicious_2019]. These items mix cognitive estimations with affective evaluations, complicating the interpretation of what respondents perceive versus what they morally reject. As a result, the conceptual clarity between perceived inequality and inequality aversion remains blurred in many empirical studies. To address this limitation, recent work has emphasized the need to distinguish between absolute and comparative measures, as well as between ideal and actual estimates of economic gaps [@garcia-sanchez_creencias_2022; @auspurg_why_2017].

## Perception of meritocracy

>>>>

# Market justice preferences

@@

Empirical studies have shown different strategies for the study of market justice preferences. A common approach in the literature is to gauge attitudes toward the legitimacy of inequality in specific domains, especially when linked to income differences. This can be traced to the seminal work of Kluegel and Smith [-@kluegel_beliefs_1981] who assessed the normative foundations that explain public support for economic inequality. Over time, this approach has been extended beyond income to include other market-mediated outcomes, such as education, healthcare, and/or pensions. For example, @vondemknesebeck_are_2016 and Immergut and Schneider [-@immergut_it_2020] examine whether citizens consider it fair that individuals with higher incomes can access better healthcare, while Lee and Stacey [-@lee_fairness_2023] apply a similar method in the context of education in Australia. These studies usually rely on survey items asking respondents to evaluate the fairness of income-based access to welfare and social services[@svallfors_political_2007;@lindh_public_2015]. More recently, Castillo et al. [-@castillo_socialization_2024] introduced a single-item composite measure of market justice to assess student attitudes toward income-based access to education, healthcare, and pensions in Chile. Such empirical strategies aim to capture the extent to which individuals accept inequality when framed as a reflection of market outcomes.

The study of market justice preferences has increasingly focused on how they are shaped by individuals' socioeconomic position, normative beliefs, and the institutional context in which they are embedded [@pierson_when_1993]. Across the literature, there is empirical evidence suggesting that individuals in more advantaged socioeconomic positions---those with higher occupational class, income, and education---are more likely to support market justice principles [@svallfors_political_2007; @koos_moral_2019; @lindh_public_2015]. This tendency reflects not only material self-interest but also a broader moral economy, in which winners of the market system internalize justifications for the status quo. At the same time, political ideology also plays a role ---such as economically conservative values ---  where  right-wing individuals show higher support for meritocracy and more skepticism towards redistribution. This is particularly salient in countries with more restricted public provision of social services. For example, in cases such as Chile [@castillo_socialization_2024] and Australia[@lee_fairness_2023] the evidence suggests that right-wing individuals are more supportive of market-based distribution of welfare. Regarding contextual factors, in liberal welfare regimes like those of the United States or the United Kingdom, market justice preferences are more widespread, while in coordinated or social-democratic regimes---such as Sweden or Germany---citizens are generally more critical of market-based inequalities [@immergut_it_2020; @lindh_public_2015].

# Perceptions of inequality and meritocracy

_The perception of economic inequality_

@@

Perceptions of inequality have been associated with a range of distributive attitudes [@castillo_perception_2022; @garcia-sanchez_vicious_2019; @trump_income_2018; @mccall_exposure_2017]. Research indicates that perceptions of inequality influence redistributive preferences to a greater extent than objective or actual economic inequality [@gimpelson_misperceiving_2018; @Castillo2011]. Lower perceived inequality can reinforce support for market-based distributive arrangements [@kuhn_eye_2011]. In contrast, when inequality is perceived as excessive, individuals could question the legitimacy of market justice and become more supportive of redistributive policies [@garcia-sanchez_vicious_2019].

Assessing the perception of inequality in empirical research is an ongoing challenge. Specifically in survey research, the assessment of perceived inequality through Likert-type items such as "income differences are too large" have been questioned as they captures general concern or discomfort rather than a specific perception [@Castillo2011; @garcia-sanchez_vicious_2019]. As a result, the conceptual clarity between perceived inequality and inequality aversion remains blurred in many empirical studies. To address this limitation, recent work has emphasized the need to distinguish between absolute and comparative measures, as well as between ideal and perceived estimates of economic gaps [@garcia-sanchez_creencias_2022; @auspurg_why_2017]. Through asking perceived salaries for occupations in the extremes of the status continuum (such as a CEO and a manual worker), an indirect measure of perceived inequality is built by the ratio of the high and the low status occupation. This type of measure provides a concrete frame that respondents can relate to more easily than abstract questions about national income distribution [@castillo_percepcion_2019; @easterbrook_social_2021; @willis_legitimacy_2015]. Evidence to dat shows that perceived wage gaps are strong predictors of political attitudes [@pedersen_attitudes_2019; @garcia-sanchez_perceptions_2018], making them a valuable tool for understanding public responses to economic disparities.

_Perception of meritocracy_

### 2025-08-05 resubmission/paper-resubmit.qmd
review introduction & antecedentes

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
  docx:
    number-sections: true
  pdf: 
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/merit-edjust.bib"
# csl: "input/bib/apa6.csl"
csl: "../input/bib/harvard.csl"
author:
  - name: Juan Carlos Castillo
    corresponding: true
    orcid: 0000-0003-1265-7854
    email: juancastillov@uchile.cl
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
  - name: Andreas Laffert
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 4
  - name: Kevin Carrasco
    orcid: 0000-0002-9348-8361
    email: kevin.carrasco@ug.uchile.cl
    affiliations:
      - ref: 2
  - name: Julio Iturra-Sanhueza
    orcid: 0000-0003-1993-3479
    email: julioiturrasanhueza@gmail.com 
    affiliations:
      - ref: 5     
affiliations: 
  - id: 1
    name: Departamento de Sociología, Universidad de Chile
  - id: 2
    name: Centro de estudios del conflicto y cohesión social (COES)
  - id: 3
    name: Núcleo milenio de desigualdades y oportunidades digitales (NUDOS)
  - id: 4
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
  - id: 5
    name: International Graduate School of Social Sciencies (BIGSSS), University of Bremen, Germany
citeproc: true
abstract: | 
  This study investigates the relationship between perceptions of economic inequality, meritocratic perceptions, and preferences for market justice in Chile between 2016 and 2023. Using six waves of panel data from the Chilean Longitudinal Social Survey - ELSOC ($N_{observations}$ = 8,643; $N_{individuals}$ = 1,687), the analysis examines how subjective assessments of inequality shape attitudes toward the role of merit in access to key social services such as healthcare, education, and pensions. Results indicate that rising perceptions of inequality are associated with lower support for market justice; however, individuals with strong meritocratic convictions are more likely to legitimize existing disparities. The study also considers the influence of major social movements during this period, which appear to have reshaped public discourse and perceptions of fairness. These findings contribute to a deeper understanding of how beliefs about justice and equity evolve in contexts marked by persistent inequality and entrenched market-oriented frameworks.
  \newline
  **Keywords**: Economic inequality, meritocracy, market justice, Chile, public preferences, inequality perception
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

>>>>

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
  docx:
    number-sections: true
  pdf: 
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/merit-edjust.bib"
# csl: "input/bib/apa6.csl"
csl: "../input/bib/harvard.csl"
author:
  - name: Juan Carlos Castillo
    corresponding: true
    orcid: 0000-0003-1265-7854
    email: juancastillov@uchile.cl
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
  - name: Andreas Laffert
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 4
  - name: Kevin Carrasco
    orcid: 0000-0002-9348-8361
    email: kevin.carrasco@ug.uchile.cl
    affiliations:
      - ref: 2
  - name: Julio Iturra-Sanhueza
    orcid: 0000-0003-1993-3479
    email: julioiturrasanhueza@gmail.com 
    affiliations:
      - ref: 5     
affiliations: 
  - id: 1
    name: Departamento de Sociología, Universidad de Chile
  - id: 2
    name: Centro de estudios del conflicto y cohesión social (COES)
  - id: 3
    name: Núcleo milenio de desigualdades y oportunidades digitales (NUDOS)
  - id: 4
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
  - id: 5
    name: International Graduate School of Social Sciencies (BIGSSS), University of Bremen, Germany
citeproc: true
abstract: | 
 Several countries have experienced a shift towards an increasing commodification and private provision of public policies, in areas such as health, education, and pensions. In Latin America, Chile stands out as a paradigmatic case of privatizations, which were strongly introduced during the military dictatorship (1973-1989), and maintained after the return of democracy. From a moral economy perspective, such institutional design has had deeply cultural consequences in terms of attitudes, ideologies and preferences towards market mechanisms. Within this framework, the present study delves into the relationship between perceptions of economic inequality, meritocratic beliefs, and market justice preferences in Chile between 2016 and 2023. Using six waves of panel data from the Chilean Longitudinal Social Survey – ELSOC (N=1,687; 8,643 observations along time), we assess whether a lower inequality perception and a higher meritocratic perception increases the preferences for private provision in health, education and pensions. The findings support the role of inequality perception, whereas the role of merit perceptions are not as straightforward. These findings contribute to a deeper understanding of how distributive beliefs evolve in contexts marked by persistent inequality and entrenched neoliberal frameworks.
  \newline
  **Keywords**: Economic inequality, meritocracy, market justice, Chile, public preferences, inequality perception
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---
